Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-14 writing/embedded_meta_learning.tex
Tweaks, details

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations. \par
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}. However, humans can use our knowledge of a task flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexibility. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity\footnote{A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.}. By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing demands. We demonstrate that our arhitectures can flexibly remap their behavior to address the meta-mapping challenge. EML may also offer other benefits, such as a useful framework for continual learning. We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems. \par

\section{Meta-mappings}
We propose the challenge of meta-mappings, that is, tasks which take tasks as an input or output. These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel. \par
We argue that these meta-mappings are a useful way to think about the flexibility that humans possess. For example, a system that learns to play go should be able to adapt to a different board size. Go on a large board or a small board share a great deal of structure, and a human can easily transfer much of their knowledge from one size to another without retraining, but deep learning models generally have no way of achieving this. Similarly, suppose an agent knows how to navigate from the airport to downtown. It should be able to adapt to changes of the environment such as street closures. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility. In particular, we can use our knowledge of a task to adapt to task alterations zero-shot, that is, without seeing a single example from the new task. \par
Meta-mappings can be cued in different ways, for example by examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to change your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board''). Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen. \par

@@

\node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(f: \text{rep} \rightarrow \text{rep}\)};

@@

\caption{Schematic of our general architecure. Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $f$ is a deep network with parameters specified by $\mathcal{H}$. Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g. both language and vision. See appendix \ref{app_model_details} for details.} \label{architecture_fig}

@@

More formally, we take a \emph{functional} perspective on learning. A datum can be represented by a constant function which outputs it. (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions. We can then interpret most machine learning tasks as a mapping of functions to functions. The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term. The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves. This is related to the idea of a homoiconic programming language, where programs can be manipulated like data. Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem. \par
Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. \par
Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs. These transformations are performed by a system with the following components (see Fig. \ref{architecture_fig} for a schematic):  

@@

\item $f: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.

@@

A basic forward pass through the system would proceed as follows. First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training). This function embedding is mapped through $\mathcal{H}$ to parameterize $f$, and then $f$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end. See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 

@@

This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$. In particular, suppose we have some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]

@@

%\subsection{Boolean functions}
%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs. Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input. We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs. \par   
%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
%
\section{Learning multivariate polynomials (very in progress)}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/poly/basic_results.png}
\caption{The system solves the meta-learning problem and successfully generalizes to held out tasks. The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model). Error-bars throughout are bootstrap 95\%-confidence intervals.}
\label{poly_basic_results}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
\caption{From examples of mapping.}
\label{poly_meta_map_results_examples}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
\caption{From language input.}
\label{poly_meta_map_results_language}
\end{subfigure}
\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples or systematic language. The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model). The system is able to execute meta-mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}). Error-bars are bootstrap 95\%-CIs.} 
\label{poly_meta_map_results}
\end{figure}
As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. \par

@@

In order to switch the system, we made a very simple change. Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state. (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues. That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game. \par   
We can train the system to identify the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. For example, if trained to play ``straight flush'' but never ``losers straight flush,'' will it nevertheless be able to adapt to trying to lose at this game, based on analogous experiences with other games? \par

@@

\caption{The system generalizes to meta-mapping new tasks. The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a novel game, it is able to apply this mapping to guess how to play the losers variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game. The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping. The system generally exceeds these baselines by a wide margin, although the switch-suits baseline is more difficult with the targeted holdout. The system is able to execute these mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}). Error-bars are bootstrap 95\%-CIs.}

@@

We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems, although it has a number of desirable characteristics. However, because of the way the architecture is factorized, it is relatively easy to change any aspect of it without altering the others. In particular, although we only considered task networks $f$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}. Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}. \par 

@@

\section{Detailed methods}
\subsection{Datasets}
\subsubsection{Polynomials} \label{meth_data_poly}
We randomly sampled the train and test polynomials as follows:
\begin{enumerate}
\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
\item Sample the subset of $k$ variables that are relevant from all the variables.
\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random coefficient drawn from $\mathcal{N}(0, 2.5)$.
\end{enumerate}
The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial. The datasets were resampled every 50 epochs of training. \par
\textbf{Meta-tasks:} For meta-tasks, we trained the network on 6 task-embedding classification tasks:
\begin{itemize}
\item Classifying polynomials as constant/non-constant.
\item Classifying polynomials as zero/non-zero intercept.
\item For each variable, identifying whether that variable was relevant to the polynomial.
\end{itemize}
We trained on 20 meta-mapping tasks, and held out 16 related meta-mappings.
\begin{itemize}
\item Squaring polynomials (where applicable).
\item Adding a constant (trained: -3, -1, 1, 3, held-out: 2, -2).
\item Multiplying by a constant (trained: -3, -1, 3, held-out: 2, -2).
\item Permuting inputs (trained: 1320, 1302, 3201, 2103, 3102, 0132, 2031, 3210, 2301, 1203, 1023, 2310, held-out: 0312, 0213, 0321, 3012, 1230, 1032, 3021, 0231, 0123, 3120, 2130, 2013).
\end{itemize}

\subsubsection{Card games}
\label{meth_data_cards}
Our card games were played with two suits, and 4 values per suit. In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands). The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available). We considered a variety of games which depend on different features of the hand: 
\begin{itemize}
\item \textbf{High card:} Highest card wins.
\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
\end{itemize}
We also considered three binary attributes that could be altered to produce variants of these games:
\begin{itemize}
\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
\item \textbf{Switch suit:} Switches which of the suits is more valuable.
\end{itemize}
Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
\textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes).
\subsection{Model \& training} \label{app_model_details}
Basic task operation:
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\item The system is trained end-to-end to minimize the loss on these outputs.
\end{enumerate}
Meta-task operation:
\begin{enumerate}
\item A meta-dataset of (input, target) task embeddings is collected. Another set (possibly only inputs) is provided.
\item The meta network $\mathcal{M}$ maps this set of (input, target) task-embedding pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The system is trained to minimize $\ell_2$ loss between these mapped embeddings and the target embeddings. 
\end{enumerate}
Note that there are two kinds of hold-out in the training of this system. First, some of the trained tasks are held-out on each training step, in order to force the system to generalize rather than just memorize. Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.

@@

@@

$f$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
$f$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $T$, $M$, $f$, and sigmoid for meta-classification outputs.} \\\hline
Main loss & \multicolumn{3}{p{8.5cm}|}{$\ell_2$ for main task \& meta-mapping, cross-entropy for meta-classification}\\\hline

>>>>

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep[e.g.][]{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations. \par
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[e.g.][]{Vinyals2016, Finn2017a}. However, humans can use our knowledge of a task flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexibility. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose a new class of architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity. (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing demands. We demonstrate that our arhitectures can flexibly remap their behavior to address the meta-mapping challenge. EML may also offer other benefits, such as a useful framework for continual learning. We suggest that approaches like EML will be key to building more intelligent and flexible deep learning systems. \par

\section{Meta-mappings}
We propose the challenge of meta-mappings, that is, tasks which take tasks as an input or output. These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel. \par
We argue that these meta-mappings are a useful way to think about human-like flexibility. For example, a go-playing system should be able to adapt to a different board size. Go on a large board and go on a small board share a great deal of structure. Humans can exploit this to play on a different board without retraining, but deep learning models generally have no way of achieving this. Similarly, suppose an agent knows how to navigate a town. It should be able to adapt to changes of the environment such as street closures. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility. Meta-mapping allows us to adapt to task alterations zero-shot, that is, without seeing a single example from the new task. \par
Meta-mappings can be cued in different ways, for example by seeing examples of similar task mappings (``you've played checkers on a regular and half-size board, now try to adapt your go strategy to a smaller board,'') or simply by natural-language instructions (``play go on this smaller board''). Achieving this kind of flexibility will be an important step towards more general intelligence -- intelligence that is not limited to exactly the training domains it has seen. \par

@@

\node [block] at (4, 3) (hyper) {\begin{tabular}{c}$\bm{\mathcal{H}}$: \textbf{Hyper} \\ \textbf{network}\end{tabular}};
\node [block, dash pattern=on 9pt off 2pt] at (0, 2) (transform) {\(F: \text{rep} \rightarrow \text{rep}\)};

@@

\caption{Schematic of our general architecure. Blocks with solid edges denote deep networks with learnable parameters, dashed edges represent inputs, outputs, embeddings, etc., and $F$ is a deep network with parameters specified by $\mathcal{H}$. Note that there may be multiple input, output, and target decoders if the system has multiple input modalities, e.g. both language and vision. See appendix \ref{app_model_details} for details.} \label{architecture_fig}

@@

More formally, we take a \emph{functional} perspective on learning. A datum can be represented by a constant function which outputs it. (For example, each point in the latent space of an autoencoder can be thought of this way.) This allows us to interpret model inputs or outputs as functions. We can then interpret most machine learning tasks as a mapping of functions to functions. The key insight is that, while these mappings could be over functions that represent data\footnote{Where ``data'' is a quite flexible term. The approach is relatively agnostic to whether the learning is supervised or reinforcement learning, whether inputs are images or natural language, etc.}, they could also operate on task-mappings themselves. This is related to the idea of a homoiconicity, defined above. Under this perspective, learning tasks, learning to map from language to tasks, and learning to flexibly transform between tasks, are all the same type of problem. \par
Specifically, we embed inputs, targets, and mappings into a shared representational space $Z$. Inputs are embedded by a deep network $\mathcal{I}: \text{input} \rightarrow Z$. Model outputs are decoded from the representational space by a deep network $\mathcal{O}: Z \rightarrow \text{output}$. Target outputs are encoded by a deep network $\mathcal{T}: \text{targets} \rightarrow Z$. Given this, the task of mapping inputs to outputs can be framed as trying to find a transformation of the representational space that takes the (embedded) inputs from the training set to embeddings that will decode to the target outputs. These transformations are performed by a system with the following components (see Fig. \ref{architecture_fig} for a schematic):  

@@

\item $F: Z \rightarrow Z$ -- the transformation, implemented by a deep network parameterized by $\mathcal{H}$.

@@

A basic forward pass through the system would proceed as follows. First, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. Some of these examples are fed to $\mathcal{M}$ to produce a function embedding (the remainder can be unlabeled during inference, or held-out to avoid memorization during training). This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process the remaining examples, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end. See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 

@@

This system can be trained end-to-end if labels are provided for the second set of inputs $D_2$. In particular, suppose we have some loss function $\mathfrak{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]

@@

%\subsection{Boolean functions}
%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs. Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input. We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs. \par   
%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
%
\section{Learning multivariate polynomials}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/poly/basic_results.png}
\caption{The system solves the meta-learning problem and successfully generalizes to held out tasks. The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model). Error-bars throughout are bootstrap 95\%-confidence intervals.}
\label{poly_basic_results}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
\caption{From examples of mapping.}
\label{poly_meta_map_results_examples}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/language_meta_results.png}
\caption{From language input.}
\label{poly_meta_map_results_language}
\end{subfigure}
\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings from seeing examples or systematic language. The solid line indicates optimal performance; the dashed line indicates chance performance (an untrained model). The system is able to execute meta-mappings either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}). Error-bars are bootstrap 95\%-CIs.} 
\label{poly_meta_map_results}
\end{figure}
As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. Details of architecture and training can be found in appendix \ref{app_detailed_methods}.\par

@@

In order to adapt the EML architecture, we made a very simple change. Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state. (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues. That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game. We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. Details of architecture and training can be found in appendix \ref{app_detailed_methods}. \par

@@

\caption{The system generalizes to meta-mapping new tasks in the cards domain. The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to novel tasks it has not been trained on. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a novel game, it is able to apply this mapping to guess how to play the losers variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game. The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping. The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout. The meta-mappings can be cued either from examples (\subref{cards_meta_map_results_examples}) or from language cues (\subref{cards_meta_map_results_language}). Error-bars are bootstrap 95\%-CIs.}

@@

We do not necessarily believe that the particular architecture we have suggested is the best architecture for addressing these problems generally, although it has a number of desirable characteristics. However, because of the way the architecture is modularized, it is relatively easy to change any aspect of it without altering the others. In particular, although we only considered task networks $F$ that are feed-forward and of a fixed depth, this could be replaced with a recurrent architecture to allow more adaptive computation, or even a more complex architecture \citep[e.g.][]{Reed2015, Graves2016}. Our work also opens the possibility of doing unsupervised learning over function representations for further learning, which relates to long-standing ideas in cognitive science about how humans represent knowledge \citep{Clark1993}. \par 

@@

\section{Detailed methods} \label{app_detailed_methods}
\subsection{Datasets}
\subsubsection{Polynomials} \label{meth_data_poly}
We randomly sampled the train and test polynomials as follows:
\begin{enumerate}
\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
\item Sample the subset of $k$ variables that are relevant from all the variables.
\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random coefficient drawn from $\mathcal{N}(0, 2.5)$.
\end{enumerate}
The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial. The datasets were resampled every 50 epochs of training. \par
\textbf{Meta-tasks:} For meta-tasks, we trained the network on 6 task-embedding classification tasks:
\begin{itemize}
\item Classifying polynomials as constant/non-constant.
\item Classifying polynomials as zero/non-zero intercept.
\item For each variable, identifying whether that variable was relevant to the polynomial.
\end{itemize}
We trained on 20 meta-mapping tasks, and held out 16 related meta-mappings.
\begin{itemize}
\item Squaring polynomials (where applicable).
\item Adding a constant (trained: -3, -1, 1, 3, held-out: 2, -2).
\item Multiplying by a constant (trained: -3, -1, 3, held-out: 2, -2).
\item Permuting inputs (trained: 1320, 1302, 3201, 2103, 3102, 0132, 2031, 3210, 2301, 1203, 1023, 2310, held-out: 0312, 0213, 0321, 3012, 1230, 1032, 3021, 0231, 0123, 3120, 2130, 2013).
\end{itemize}
\textbf{Language:} We encoded the meta-tasks in language by sequences as follows:
\begin{itemize}
\item Classifying polynomials as constant/non-constant: \verb|[``is'', ``constant'']|
\item Classifying polynomials as zero/non-zero intercept: \verb|[``is'', ``intercept_nonzero'']|
\item For each variable, identifying whether that variable was relevant to the polynomial: \verb|[``is'', <variable-name>, ``relevant'']|
\item Squaring polynomials: \verb|[``square'']|
\item Adding a constant: \verb|[``add'', <value>]|
\item Multiplying by a constant: \verb|[``multiply'', <value>]|
\item Permuting inputs: 
\begin{verbatim}[``permute'', <variable-name>, <variable-name>, <variable-name>, 
<variable-name>]\end{verbatim}
\end{itemize}
All sequences were front-padded with ``<PAD>'' to the length of the longest sequence.

\subsubsection{Card games}
\label{meth_data_cards}
Our card games were played with two suits, and 4 values per suit. In our setup, each hand in a game has a win probability (proportional to how it ranks against all other possible hands). The agent is dealt a hand, and then has to choose to bet 0, 1, or 2 (the three actions it has available). We considered a variety of games which depend on different features of the hand: 
\begin{itemize}
\item \textbf{High card:} Highest card wins.
\item \textbf{Pairs} Same as high card, except pairs are more valuable, and same suit pairs are even more valuable.
\item \textbf{Straight flush:} Most valuable is adjacent numbers in same suit, i.e. 4 and 3 in most valuable suit wins every time (royal flush).
\item \textbf{Match:} the hand with cards that differ least in value (suit counts as 0.5 pt difference) wins.
\item \textbf{Blackjack:} The hand's value increases with the sum of the cards until it crosses 5, at which point the player ``goes bust,'' and the value becomes negative. 
We also considered three binary attributes that could be altered to produce variants of these games:
\begin{itemize}
\item \textbf{Losers:} Try to lose instead of winning! Reverses the ranking of hands.
\item \textbf{Suits rule:} Instead of suits being less important than values, they are more important (essentially flipping the role of suit and value in most games).
\item \textbf{Switch suit:} Switches which of the suits is more valuable.
Any combination of these options can be applied to any of the 5 games, yielding 40 possible games. The systems were trained with the full 40 possible games, but after training we discovered that the ``suits rule'' option does not substantially alter the games we chose (in the sense that the probability of a hand winning in the two variants of a game is very highly correlated), so we have omitted it from our analyses.\par
\textbf{Meta-tasks:} For meta-tasks, we gave the network 8 task-embedding classification tasks (one-vs-all classification of each of the 5 game types, and of each of the 3 attributes), and 3 meta-mapping tasks (each of the 3 attributes). \par
\textbf{Language:} We encoded the meta-tasks in language by sequences of the form \verb|[``toggle'', <attribute-name>]| for the meta-mapping tasks, and \verb|[``is'', <attribute-or-game-name>]|.
\subsection{Model \& training} \label{app_model_details}
\textbf{Basic task operation:}
\begin{enumerate}
\item A training dataset $D_1$ of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs $D_2$ is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $F$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\item The system is trained end-to-end to minimize the loss on these outputs.
\end{enumerate}
The model is trained to minimize 
\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_i\right), \mathcal{T}\left(y_i\right) \right) \text{ for } (x_i, y_i) \in D_1 \right\}\right)\right)\]
\textbf{Meta-task operation:}
\begin{enumerate}
\item A meta-dataset of (source-task-embedding, target-task-embedding) pairs, $D_1$, is collected. Another dataset $D_2$ (possibly only source tasks) is provided.
\item The meta network $\mathcal{M}$ maps this set of (source, target) task-embedding pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $F$, which is used to transform the second set of inputs to a set of output embeddings.
\item The system is trained to minimize $\ell_2$ loss between these mapped embeddings and the target embeddings. 
\end{enumerate}
The model is trained to minimize
\[\mathbb{E}_{(z_{source}, z_{target})\in {D}_2} \left[ \mathfrak{L}\left(z_{target}, f_{D_1}\left(\mathcal{I} \left(z_{source}\right)\right) \right)\right]\]
where $\mathfrak{L}$ is $\ell_2$ loss, and $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left((z_{source},z_{target}\right) \in D_1 \right\}\right)\right)\]
Note that there are two kinds of hold-out in the training of this system. First, some of the trained tasks are held-out on each training step (i.e. $D_2$), in order to force the system to generalize rather than just memorize. Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training.

@@

$\mathcal{L}$ architecture & \multicolumn{1}{p{2.5cm}|}{2-layer LSTM + 2 fully-connected} & - & \multicolumn{1}{p{2.5cm}|}{1-layer LSTM + 2 fully-connected} \\\hline 
$\mathcal{L}$ num. hidden units & 512 & - & 512 \\\hline 

@@

$F$ architecture & \multicolumn{3}{c|}{4 layers} \\\hline 
$F$ num. hidden units & \multicolumn{3}{c|}{64} \\\hline 
Nonlinearities & \multicolumn{3}{p{8.5cm}|}{Leaky ReLU in most places, except no non-linearity at final layer of $\mathcal{T}$, $\mathcal{M}$, $\mathcal{L}$, $F$, and sigmoid for meta-classification outputs.} \\\hline
Main loss & \multicolumn{3}{p{8.5cm}|}{$\ell_2$ for main task \& meta-mapping, cross-entropy for meta-classification.}\\\hline
